Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
slightly rephrase

Judging by their common characteristics and the available implementations, spatial partitioning methods can be coarsely categorized into (1) buffering, (2) blocking and (3) clustering methods.
If a method had the potential to belong to multiple categories, a deliberate category assignment was made for one specific group which matched the main characteristic of the respective method best.

>>>>

Spatial partitioning methods can be roughly divided into three groups: (1) buffering, (2) blocking and (3) clustering methods (Table \@ref(tab:sptcv-methods)).
If a method could have been placed into multiple categories, we deliberately assigned the group which matched best the main characteristic of the respective method.
